Exploring Income Inequality Dynamics in Canada: A Geospatial and Temporal Analysis

### 2024-04-16 paper/paper.qmd
upload the pdf

In Model (\ref{eq-model1})is specified as follows:

@@

The first model (Equation 1) aims to capture the relationship between the response variable, $y_i$, representing the highest-to-lowest average income ratio of average after-tax income to the lowest decile of average after-tax income of Canada in the $i^{th}$ year and province $i$, and the predictor variables, $\text{Year}_i$ and $\text{Geographical Location}_i$.

@@

@tbl-model1

The regression results are as follows:

@@

Overall, the model's R-squared value of 0.149 indicates that approximately 14.9% of the variability in the highest-to-lowest average income ratio is explained by the predictor variables included in the model. Additionally, the adjusted R-squared value of 0.117 suggests that the model may slightly overestimate the true explanatory power due to the inclusion of additional predictors.

The log likelihood of -1934.210 indicates the goodness-of-fit of the model, with lower values indicating a better fit. Furthermore, the root mean squared error (RMSE) of 8.25 provides a measure of the model's predictive accuracy, with smaller values indicating better predictive performance.

In summary, Model 1 provides valuable insights into the factors influencing the highest-to-lowest average income ratio in Canada, highlighting the effects of time (Year) and geographical location (provinces) on income inequality. These findings contribute to a better understanding of regional disparities in income distribution and can inform policy decisions aimed at reducing inequality across different provinces.

The results of the model2 reveal several significant findings regarding the relationship between the response variable and the predictor variables. Firstly, the intercept term is estimated to be -3309430.66, indicating the expected value of the response variable when all other predictors are zero. This intercept provides a reference point for comparison and interpretation of the effects of the other predictor variables.

@@

In summary, the results provide valuable insights into the factors influencing the response variable, as well as the overall fit and predictive performance of the model. These findings contribute to a better understanding of the relationships between the predictor variables and the response variable, which can inform decision-making and policy development in relevant contexts.

@@

One weakness of this study is the potential for omitted variable bias. Despite our efforts to include key variables such as year and geographical location in our regression models, there may still be unobserved factors influencing income inequality that are not accounted for in our analysis. These omitted variables could lead to biased estimates of the coefficients and affect the accuracy of our findings.

>>>>

In Model (\ref{eq-model1}) is specified as follows:

@@

The first model (\ref{eq-model1}) aims to capture the relationship between the response variable, $y_i$, representing the highest-to-lowest average income ratio of average after-tax income to the lowest decile of average after-tax income of Canada in the $i^{th}$ year and province $i$, and the predictor variables, $\text{Year}_i$ and $\text{Geographical Location}_i$.

@@

Based on @tbl-model1, the regression outcomes are outlined as follows:

@@

Overall, the model's R-squared value of 0.149 indicates that approximately 14.9% of the variability in the highest-to-lowest average income ratio is explained by the predictor variables included in the model. Additionally, the adjusted R-squared value of 0.117 suggests that the model may slightly overestimate the true explanatory power due to the inclusion of additional predictors. The log likelihood of -1934.210 indicates the goodness-of-fit of the model, with lower values indicating a better fit. Furthermore, the root mean squared error (RMSE) of 8.25 provides a measure of the model's predictive accuracy, with smaller values indicating better predictive performance.

Combined with @figure5, Model 1 provides valuable insights into the factors influencing the highest-to-lowest average income ratio in Canada, highlighting the effects of time (Year) and geographical location (provinces) on income inequality.

The results of the Model 2 reveal several significant findings regarding the relationship between the response variable and the predictor variables. Firstly, the intercept term is estimated to be -3309430.66, indicating the expected value of the response variable when all other predictors are zero. This intercept provides a reference point for comparison and interpretation of the effects of the other predictor variables.

@@

@@

One weakness of this study is the potential for omitted variable bias. Despite our efforts to include key variables such as year and geographical location in our regression models, there remains a possibility of unaccounted factors, such as gender and education, influencing income inequality. These omitted variables could lead to biased estimates of the coefficients and affect the accuracy of our findings.
